Dynamic Transition Analysis with TIMES

### 2019-01-15 doc/2019-01-poster/poster.tex
changed plot sizes
Former-commit-id: 2c4e4bed8cf810e96bb2e7f6e03419136e2b2c03 [formerly fc227173353422fcc65b0dfb240ca0c8856e7964]
Former-commit-id: 7b2a73d86c7662951e700189a55c75f167ddc0c5
updated UIUC logo
Former-commit-id: 62c116882761f2fbf64d33495f1fc9c6f3dc17f9 [formerly 3416457406c39478f85bf2d64e5fb07f260ab827]
Former-commit-id: b8ee3fa6347c948186bbae81961f728fd0a106d4

%----------------------------------------------------------------------------------------
%	TAKE AWAY
%----------------------------------------------------------------------------------------
\begin{figure}[H] 
\centering
\includegraphics[scale=1.4]{cost}
\caption{Cost variation in solar, wind, and photocatalytic H$_2$ production.}
\label{cost}
\end{figure}
         \begin{alertblock}{Take Aways}
	\begin{itemize}
                \item Nuclear power is the cleanest and cheapest.

@@

%\vspace{10mm}
\begin{center}
\begin{tabular}{cccc}
\includegraphics[scale=0.5]{arfc_logo.png} & \includegraphics[scale=0.5]{wpi_logo.png} & \includegraphics[scale=0.1]{ku_logo.png} &\includegraphics[scale=0.7]{i2cner_logo.png}
%\includegraphics[width=\linewidth, height=0.1\textheight]{i2cner_logo.png}
\end{tabular}
\end{center}

>>>>

%----------------------------------------------------------------------------------------
%	TAKE AWAY
%----------------------------------------------------------------------------------------
\begin{figure}[H] 
\centering
\includegraphics[scale=1.6]{cost}
\caption{Cost variation in solar, wind, and photocatalytic H$_2$ production.}
\label{cost}
\end{figure}
         \begin{alertblock}{Take Aways}
	\begin{itemize}
                \item Nuclear power is the cleanest and cheapest.

@@

%\vspace{10mm}
\begin{center}
\begin{tabular}{cccc}
\includegraphics[scale=0.7]{arfc_logo.png} & \includegraphics[scale=0.5]{wpi_logo.png} & \includegraphics[scale=0.1]{ku_logo.png} &\includegraphics[scale=0.7]{i2cner_logo.png}
%\includegraphics[width=\linewidth, height=0.1\textheight]{i2cner_logo.png}
\end{tabular}
\end{center}
